### 2013-11-22 PositionPaper/incremental.tex

%-----------------------------------------------------------------
\subsection{Query Rewriting}
\label{sec:queryRew}
%-----------------------------------------------------------------
%{\color{red}
%Here Martin will explain the rewriting problem.
%}

See wether a similar Q has been already rewritten or rewrite it. Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.   The subsueries represent the possible combination of services that can answer the initial query with given SLA.

>>>>

%-----------------------------------------------------------------
\subsection{Query Rewriting}
\label{sec:queryRew}
%-----------------------------------------------------------------
{\color{red}
See wether a similar Q has been already rewritten or rewrite it. Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.   The subqueries represent the possible combination of services that can answer the initial query with given SLA.
}
